---
title: "Week-11:diary entry+Placeholders integrated with webpage"
author: "Wang Renhe"
date: "30-10-2023"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

**Question 1:** 
What is the topic that you have finalized?

**Solution:** 
current topic: Homicide rate in US from 2001-2010.
It can help us understand of and prevent future crime, for the welfare of the society. 

**Question 2.** 
What are the data sources that you have curated so far?

**Solution:** 
I get this data set from Kaggle

```{r,echo=TRUE,eval=TRUE}
library(tidyverse)
homicide <- read.csv("database2.csv")
head(homicide)
```

**Week10-Continue from Week9**

### What is the question that you are going to answer?
How do the victim-murderer relationship and the age of perpetrators impact the choice of weapons used in homicides?

### Why is this an important question?
A research conducted by American Journal of Preventive Medicine suggest a rising trend in intimate partner homicides, as well as a higher occurrence of homicides involving friends, acquaintances, and even strangers. Those findings underscore the importance of relevant laws.

From Bailey et al.(2023), urban areas exhibit a higher propensity for the escalation of gun violence as compared to other weapon-related incidents, identify the pivotal age group can effectively establish deployment strategies, so can prevent future trauma.

According to United Nations, reduce the crime rate will reduce potential harmful effects on individuals and society. 


### Which rows and columns of the dataset will be used to answer this question?
Year, Perpetrator Age, Relationship, Weapon

### Include the challenges and errors that you faced and how you overcame them
First, data entry errors may occur when there are missing values or incorrect data entries, which can distort the dataset and affect the accuracy of the results. Hence, it is necessary to address missing values by removing them from the dataset before conducting any analysis.
Secondly, if outliers exist, the unusual or erroneous data points can significantly impact statistical analysis. Therefore, I will try to highlight those values and see if I should exclude or include them in the analysis. Moreover, incorrect data transformations can lead to inaccurate results because linear regression can be used with a combination of categorical and numerical values. To address this, it's essential to apply suitable data transformation techniques to incorporate categorical variables correctly into the analysis.

**Week11**

### (1) List the visualizations that you are going to use in your project (Answer: What are the variables that you are going to plot? How will it answer your larger question?)

plot charts of two sets of variables from 2010-2014(one for each year): 

1. "Relationship" and "Weapon": I will plot graphs for weapon types and the different murder-victim relationships. After plotting graphs for all weapons, I will combine all 

By knowing this, this can show me if there is any pattern between the victim-murder relationship and weapon use during homicide. And this will answer my larger question. If yes, then we will know how to comprehense the law and restrict consumption for certain weapons. Meanwhile, we will also being informed what kind of weapon can be avoid, i.e. knife should be kept away or only accessible by them, so that they can protect themselves.If no then, it means no significance relationship between, hence, all weapons should be treated equally dangerous

2. "Perpetrator Age" and "Weapon". However, as age varies differently, in order to better analyse the trend, I will divide them into various intervals: "<14"15-17""18-21""22-24""25-29""30-34""35-39""40-49"">50"

If there is a relationship between Age and Weapon used during homicide. It will answer the larger question. If yes, then maybe younger generation prefer one weapon over the other.
